Asymmetric relationships and their effects on coexistence

### 2023-07-17 paper/Paper.Rnw
added citation for stat

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig1_a-h.pdf}
\caption{Examples motivating our study of the effects of asymmetric tail associations (ATAs) on competition
and coexistence. (a-c) Bivariate random variables with standard normal marginals showing
alternative patterns of association in the left and right parts of the distributions. 
The two variables in (a) are more strongly related to each
other in the left parts of the distributions, termed ``left-tail association;'' those in (b) 
are symmetrically associated; and those in (c) 
are more strongly related to each other in the right parts, termed ``right-tail association''. All three cases have 
the same Pearson correlation, $\rho$, up to sampling variation, so Pearson correlation does not identify these 
very different patterns of association. For (a, c), we used asymmetrically tail associated cases which are perfectly 
correlated in the lower or upper halves of the distributions, though it is also possible to generate asymmetrically 
tail associated noise with imperfect correlations in both halves of the distributions [\citealp{Nelsen2006,Ghosh_2020_AER};
see also (d,e)]. 
The variables $(B_1,B_2)$ described in the Introduction and Methods were obtained by generating noise as 
pictured and then transforming the marginals as specified in Methods.
(d,e) Two examples of ATAs found in nature. Axes are population densities of two plankton species, 
\emph{Ceratium fusus} and \emph{Ceratium furca}, sampled in successive years in two of the 15 locations 
in the North Sea considered by \citep{Ghosh_2020_ecolevol}. ATAs differed by location: 
(d) has a partial Spearman correlation of  \Sexpr{round(plankStats$d,3)}, indicating left-tail association
 and (e) has a partial Spearman correlation of  \Sexpr{round(plankStats$e,3)}, indicating right-tail association.
(f-h) Lottery model population simulations using $(B_1,B_2)$ obtained by transforming the 
respectively corresponding variables (a-c; see Introduction).
\label{fig:pedagog1}}
\end{figure}

>>>>

\begin{figure}
\includegraphics[width=\textwidth]{../results_figs/fig1_a-h.pdf}
\caption{Examples motivating our study of the effects of asymmetric tail associations (ATAs) on competition
and coexistence. (a-c) Bivariate random variables with standard normal marginals showing
alternative patterns of association in the left and right parts of the distributions. 
The two variables in (a) are more strongly related to each
other in the left parts of the distributions, termed ``left-tail association;'' those in (b) 
are symmetrically associated; and those in (c) 
are more strongly related to each other in the right parts, termed ``right-tail association''. All three cases have 
the same Pearson correlation, $\rho$, up to sampling variation, so Pearson correlation does not identify these 
very different patterns of association. For (a, c), we used asymmetrically tail associated cases which are perfectly 
correlated in the lower or upper halves of the distributions, though it is also possible to generate asymmetrically 
tail associated noise with imperfect correlations in both halves of the distributions [\citealp{Nelsen2006,Ghosh_2020_AER};
see also (d,e)]. 
The variables $(B_1,B_2)$ described in the Introduction and Methods were obtained by generating noise as 
pictured and then transforming the marginals as specified in Methods.
(d,e) Two examples of ATAs found in nature. Axes are population densities of two plankton species, 
\emph{Ceratium fusus} and \emph{Ceratium furca}, sampled in successive years in two of the 15 locations 
in the North Sea considered by \citep{Ghosh_2020_ecolevol}. ATAs differed by location: 
(d) has a partial Spearman correlation of  \Sexpr{round(plankStats$d,3)}, indicating left-tail association
 and (e) has a partial Spearman correlation of  \Sexpr{round(plankStats$e,3)}, indicating right-tail association \cite{Ghosh_2020_AER}.
(f-h) Lottery model population simulations using $(B_1,B_2)$ obtained by transforming the 
respectively corresponding variables (a-c; see Introduction).
\label{fig:pedagog1}}
\end{figure}
